Low Complexity Adaptive Beamformer\\ for Active Sonar Imaging

### 2015-10-14 LCAforActiveSonarImaging/lca.tex
la2pdf commit - 2015:10:14	14:39:08	(Wed14.Oct)

A much faster and simpler alternative to MVDR is the Low Complexity Adaptive (LCA) beamformer. It was first introduced by Synnev\aa{}g in clinical medical imaging~\cite{Synnevag2008}, who demonstrated its ability to obtain very similar image quality to MVDR in a system with focused transmit beams\todo{ha med at i US \o{}nsker man ulike vindus-typer p\aa{} forskjellig range?}. LCA applies a set of predefined windows, or tapers, and selects the one offering the best noise suppression. It relies on the same optimization criterion as MVDR, thus may be considered a version of MVDR with a reduced window solution space. Alternatively, it may be viewed as a delay-and-sum (DAS) beamformer with an adaptive multi-taper extension. Such extensions up to 3 windows by e.g. Stankwitz in radar imaging~\cite{Stankwitz1995}, but unlike these LCA more windows, and add micro-steered variations of them.

>>>>

A much faster and simpler alternative to MVDR is the Low Complexity Adaptive (LCA) beamformer. Based on an idea by Vignon~\cite{Vignon2008}, it was first introduced by Synnev\aa{}g in clinical medical imaging~\cite{Synnevag2008}, who demonstrated its ability to obtain very similar image quality to MVDR in a system with focused transmit beams\todo{ha med at i US \o{}nsker man ulike vindus-typer p\aa{} forskjellig range?}. LCA applies a set of predefined windows, or tapers, and selects the one offering the best sidelobe suppression. It relies on the same optimization criterion as MVDR, thus may be considered a version of MVDR with a reduced window solution space. Alternatively, it may be viewed as a delay-and-sum (DAS) beamformer with an adaptive multi-taper extension. Such extensions up to 3 windows by e.g. Stankwitz in radar imaging~\cite{Stankwitz1995}, but unlike these LCA more windows, and add micro-steered variations of them.
